Old or Heavy?\\Decaying Gracefully with Age/Weight Shapes.

### 2019-03-04 papers/CADE19/paper.tex
proofread, tidy up

\documentclass{llncs}
\usepackage{graphicx}
\usepackage[caption=false]{subfig}
\usepackage[dvipsnames]{xcolor}
\usepackage{amssymb}
\usepackage{amsmath}

@@

We restrict our attention to clause selection strategies that alternate between selecting clauses based on age (e.g. in a first-in-first-out manner) and weight (e.g. those with the fewest symbols first).
It was confirmed by \sandm{} that alternating these two heuristics outperforms either by itself.
We refer to the ratio with which we use either heuristic as the \emph{age/weight ratio} (AWR) as this is the terminology employed by the Vampire theorem prover, which we use as a vehicle for our study.

@@

\section{Conclusions and Future Work}
\label{sec:conclusions}

>>>>

\documentclass{llncs}
\usepackage{graphicx}
\usepackage[caption=false]{subfig}
\usepackage{amssymb}
\usepackage{amsmath}

@@

We restrict our attention to clause selection strategies that alternate between selecting clauses based on age (i.e. in a first-in-first-out manner) and weight (i.e. those with the fewest symbols first).
It was confirmed by \sandm{} that alternating these two heuristics outperforms either by itself.
We refer to the ratio with which we use either heuristic as the \emph{age/weight ratio} (AWR) as this is the terminology employed by the Vampire theorem prover, which we use as a vehicle for our study.

@@

%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison with other Solvers}

\begin{table}[t]
	\caption{
Total number of problems solved compared to other solvers.
}
	\centering
	\begin{tabular}{l l l}
	Solver~~ & Total solved~~~ & Uniquely solved \\
	\hline
	Vampire (old)	& 13,057 & 0\\
	Vampire (new)   & 13,191 & 54\\
	E 		& 10,845 & 190\\
	iProver		& 8,143 & 215\\
	CVC4		& 9,354 & 501\\
	\end{tabular}
	\label{tab:other}
\end{table}

To place these results in context, we compare the overall number of problems solved by our new strategies with the results of other solvers, using their 2018 CASC competition mode.
These results are from 300-second runs in identical conditions and are given in Table~\ref{tab:other}.
In this table \emph{Vampire (old)} stands for the 2018 competition version whilst \emph{Vampire (new)} stands for the union of all problems solved by new options in the previous section.
Between them, the two versions of Vampire solve 1,030 problems uniquely.
54 unique problems found in the previous section remain unique when compared to other competitive solvers.

%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}
\label{sec:conclusions}
